---
title: "Marketing Strategies - CarreFour"
author: "Tom_Kinyanjui_Njoroge"
date: "July 25, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Defining the question 
To come up with factual information on which marketing strategies carrefour should adopt based on the the analysis of the provided data.

##Metric of Success
Build a model that will analyze on the relevant marketing strategies to be adopted by the organization 

# loading the data
```{r}
# Data for Analysis, Dimension Reduction and Feature Selection
sales <- read.csv("file:///C:/Users/HP/Downloads/Supermarket_Dataset_1 - Sales Data.csv")
head(sales)
```

# Check the Data
```{r}
dim(sales)
```

```{r}
#Unique value counts
table(sales$Branch)
table(sales$Customer.type)
table(sales$Gender)
table(sales$Product.line)
table(sales$Payment)
#Convert to Factor
library(dplyr)
sales <- mutate_at(sales, vars(Branch, Customer.type,Gender,Product.line,Payment), as.factor)
str(sales)
```

# Data Cleaning
```{r}
# Droppig irrerevant column
sales_new <- sales[,-1]
head(sales_new)
```

```{r}
lower <- function(x) {
    colnames(x) <- tolower(colnames(x))
    x
}
sales_new <- lower(sales_new)
head(sales_new)
```

```{r}
colSums(is.na(sales_new))
```

```{r}
sales_new <- unique(sales_new)
dim(sales_new)
```

```{r}
#Outliers
num_col <- sales_new[, c(5,6,7,11,12,13,14,15)]
outlier = function(x){
  for(i in colnames(x)){
    boxplot(sales_new[[i]], xlab=i, main=paste0("Boxplot for ",i))
  }
}
outlier(num_col)
```


```{r}
#remove outliers 
outlier_replace <- function(x){
   qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
   caps <- quantile(x, probs=c(.05, .95), na.rm = T)
   H <- 1.5 * IQR(x, na.rm = T)
   x[x < (qnt[1] - H)] <- caps[1]
   x[x > (qnt[2] + H)] <- caps[2]
   return(x)}
sales_new$tax <-outlier_replace(sales_new$tax)
sales_new$cogs <- outlier_replace(sales_new$cogs)
sales_new$gross.income <- outlier_replace(sales_new$gross.income)
sales_new$total <- outlier_replace(sales_new$total)
outlier(num_col)
```

# EDA
## Univariate
```{r}
library(Hmisc)
describe(num_col)
```

```{r Histogram}
histogram = function(x){
  for(i in colnames(x)){
    hist(sales_new[[i]], breaks = 10,main =i,xlab = i,col = "dodgerblue")
  }
}
histogram(num_col)
```

## Bivariate

```{r}
#correlation 
corr <- sales_new[, c(-1,-2,-3,-4,-8,-9,-10,-12)]
correlation_matrix <- cor(corr)
library(corrplot)
corr_data <- as.data.frame(correlation_matrix)
corr_data
corr <- corrplot(correlation_matrix, method = "shade",order = "hclust", col=colorRampPalette(c("yellow","green","navyblue"))(100), addgrid.col="gray", tl.col = "black", tl.cex = 0.7,tl.srt = 45)
```

```{r}
#scatter plot
plot(sales_new$gross.income, sales_new$cogs, main = "Relationship between COGS and Gross Income", xlab="Gross Income", ylab="COGS")
plot(sales_new$total, sales_new$gross.income, main = "Total Sales vs. Gross Income ", xlab = "Total Sales", ylab = "Gross Income")
plot(sales_new$total, sales_new$rating, main = "Total Sales vs. Rating", xlab = "Total Sales", ylab = "Rating")
```
# Implement the Solution
#Using PCA 
```{r}
pred <- sales_new[, c(-1,-2,-3,-4,-8,-9,-10,-12,-15)]
sales.pca <- prcomp(pred, scale. = TRUE, center = TRUE)
summary(sales.pca)
label <- sales_new[, "total"]
library(ggbiplot)
ggbiplot(sales.pca, obs.scale = 1.2,var.scale=1.3)
ggbiplot(sales.pca, choices = c(3,4) ,obs.scale = 1.2, var.scale = 1.3)
```

## Feature Selection
```{r}
library(caret)
correlation = cor(pred)
highly <- findCorrelation(correlation, cutoff = 0.75)
# highly correlated variables
names(pred[,highly])
# Dataset without the Highly Correlated
new_df <- pred[-highly]

par(mfrow = c(1, 2))
corrplot(correlation, order = "hclust",tl.col = "black", tl.cex = 0.7)
corrplot(cor(sales_new1), order = "hclust",tl.col = "black", tl.cex = 0.7)
```
